Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exhange-Correlation Functional

### 2025-03-28 paper.tex
cleanup

%\keywords{Suggested keywords}

@@

\begin{table}[tbp]
  \caption{Characteristics of site energies $E$ (all in \unit[]{eV}) obtained for the different values of \ahfx : minimum ($E_\text{min}$) and maximum ($E_\text{max}$), the overall standard deviation and the contributions for static and polar calculations, as well as the largest absolute variation $D_{\ahfx}$ with respect to the PBE0 data ($\ahfx=0.25$).}
  \begin{ruledtabular}
    \begin{tabular}{c c c c c c c}
    $\ahfx$ & $E_\text{min}$ & $E_\text{max}$ & $\sigma$ & $\sigma_\text{el}$ & $\sigma_\text{polar}$ &  $D_{\ahfx}$ \\%  & $E_{i_\text{max}}$ \\
    \hline
    0    & -1.11 & -0.59 & 0.08 & 0.10 & 0.04 & 0.13 \\ %&  -0.94 \\
    0.05 & -1.07 & -0.63 & 0.07 & 0.09 & 0.04 & 0.12 \\ %&  -0.94 \\
    0.10 & -1.13 & -0.61 & 0.08 & 0.10 & 0.04 & 0.13 \\ %&  -0.94 \\
    0.15 & -1.16 & -0.59 & 0.09 & 0.11 & 0.05 & 0.15 \\ %&  -0.69 \\
    0.20 & -1.12 & -0.63 & 0.08 & 0.10 & 0.05 & 0.12 \\ %&  -0.82 \\
    0.25 & -1.17 & -0.60 & 0.08 & 0.11 & 0.04 & ---  \\ %&   ---\\
    \end{tabular}
  \end{ruledtabular}
  \label{tab:maxEi}
\end{table}

@@

\begin{table}[tbp]
\caption{Simulated ToF (in \unit[]{s}) for different values of \ahfx in the full graph, with an additional cutoff on $J^2$, and for the case with no energetic disorder, respectively.}
\begin{ruledtabular}
  \begin{tabular}{c c c c }
        \ahfx & full & $J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > -5)$ & $\Delta E_{ij} =0$ \\% & $v_\text{ToF}$(no $E$) \\
    \hline
        0.00 &  $6.4 \cdot 10^{-9}$ & $7.5 \cdot 10^{-9}$ & $1.9 \cdot 10^{-10}$ \\%& 42 \\
        0.05 & $ 7.9 \cdot 10^{-9}$ & $8.1 \cdot 10^{-9}$ & $4.1 \cdot 10^{-10}$ \\%& 20 \\
        0.10 & $ 1.6 \cdot 10^{-8}$ & $1.6 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\%& 20 \\
        0.15 & $ 3.0 \cdot 10^{-8}$ & $3.1 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\%& 25 \\
        0.20 & $ 2.1 \cdot 10^{-8}$ & $2.5 \cdot 10^{-8}$ & $4.5 \cdot 10^{-10}$ \\%& 18 \\
        0.25 & $ 9.5 \cdot 10^{-8}$ & $9.7 \cdot 10^{-8}$ & $7.2 \cdot 10^{-10}$ \\%& 11 \\
    \end{tabular}
\end{ruledtabular}
\label{tab:ToF_MADN_HFX}
\end{table}

From the analysis of reorganization energies, site energies, and electronic coupling elements for different values of \ahfx, it is not clear how the mostly on distribution-level observed variations impact the overall charge transport properties. To scrutinize the dependence of such a material property, we now calculate the time-of-flight $\tau$ and report the respective values in Table~\ref{tab:ToF_MADN_HFX}. Here, we refer with ''full'' to time-of-flight obtained for the the as-calculated charge transport network. One can see that $\tau$ varies by roughly one order of magnitude between $\ahfx=0$ ($\unit[6.3\cdot 10^{-9}]{s}$) and $\ahfx=0.25$ ($\unit[9.5\cdot 10^{-8}]{s}$), with an almost monotonous increase. When the squared coupling elements with values below $\unit[10^{-5}]{(eV)^2}$ are set to zero ($J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > -5)$), one obtains only minimally, but consistently, larger $\tau$, corroborating the notion that the very small coupling elements are of little relevance for charge transport. Finally, we also consider the case in which the energetic disorder is ignored ($\Delta E_{ij}=0$). Here, one also can see (next to the generally shorter time-of-flight) a consistent increase in $\tau$, however only by a factor of about \unit[3.8]{}, a combined effect of the increased reorganization energy and variations in coupling elements.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Because the precise distribution of the uncertainties of the $M$ parameters is not known, we consider the maximum amount of uncertainties from a maximum likelihood estimation based on the data obtained from the explicit results for the different values of \ahfx and the assumption of normal distributions. In other words, each of the parameters $x_i$ for $i=1,\ldots,M$ is assigned a normal distribution with $\mathcal{N}(\mathbb{E}(x_i),\mathbb{V}(x_i))$, with $\mathbb{E}(x_i)$ ($\mathbb{V}(x_i)$) the mean (variance) of the respective data. Then, Monte-Carlo sampling is used to obtain $N_\text{MC}=50000$ different realizations of $\mathbf{x}$, the respective time-of-flight is calculated from these samples, and the resulting distribution $P(\log_{10}(\tau))$ is statistically analyzed. Specifically, we consider four different settings: in three settings, only one of the parameters blocks $(\lambda,\left\{E\right\},\left\{\log_{10}(J^2)\right\})$ is sampled while the values of the other blocks are set to their respective mean values, and we denote the resulting distributions as $P_\lambda(\log_{10}(\tau))$, $P_E(\log_{10}(\tau))$, and $P_J(\log_{10}(\tau))$, respectively. In the fourth setting, all parameters are sampled at the same time, yielding $P_\mathbf{x}(\log_{10}(\tau))$. As these distributions do not necessarily follow any specific analytic form, we estimate a $99\%$ confidence interval around the median using the equal-tailed percentile method. \bjoern{Maybe discuss somewhere:}{correlations between parameters are gone, especially in site energies, but they are (practically) uncorrelated in MADN.}

%Then Monte Carlo scheme is used to estimate the distribution of the ToF. The Monte Carlo scheme has the procedure:
%\begin{enumerate}
%\item For all $i,j=1,2,\cdots, N_d$, obtain a realization $(x_1, x_2, \cdots, x_{N_d})$ where each parameter has the normal distribution, meaning the corresponding electronic parameters are sampled from the distribution $\lambda_i \in \mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$, $E_i \in \mathcal{N}(\mathbb{E}(E_i), \mathbb{V}(E_i))$, $\log_{10}(J_{ij}^2) \in \mathcal{N}(\mathbb{E}(\log_{10}(J_{ij}^2)), \mathbb{V}(\log_{10}(J_{ij}^2)))$. 
%\item Calculate ToF using the sampled data set $(x_1, x_2, \cdots, x_{Nd})$. 
%\item Repeat step 1 and 2 for $N_\text{MC} = 50000$ times to obtain ToFs. Plot the distribution of the ToFs.
%\item Estimate the 99\% confidence interval around the median.
%\end{enumerate}

%To understand how the uncertainty pass from $E, \lambda, J_{ij}$ to ToF, the parameter control is used. That is, a set of parameter, such as $E_i$ for all $i=1,2,\cdots,N$ is choose while keeping other parameter fixed, then performed Monte Carlo sampling to obtain ToF distribution and estimate upper and lower confidence bound.
%Then we use Sobol total indices to analyze and quantify 
%which uncertainty among $E, \lambda, J_{ij}$ has a greater impact on the ToF,

@@

%The distribution that we want to obtained during the parameter control are as followed:
%\begin{enumerate}
%    \item Fixed the $\lambda$ to be $\mathbb{E}(\lambda)$, and $\log_{10}(J_{ij}^2)$ to be $\mathbb{E}(\log_{10}(J_{ij}^2))$. Then each molecule energy $E_i$ is sampled from the normal distribution $\mathcal{N}(\mathbb{E}(E_i), \mathbb{V}(E_i))$. Finally obtain and plot the histogram $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|E_i \text{ uncertain})$.
%    \item Fixed all $E_i$ to be $\mathbb{E}(E_i)$ and all $\log_{10}(J_{ij}^2)$ to be $\mathbb{E}(\log_{10}(J_{ij}^2))$. Then $\lambda$ is sampled from the normal distribution $\mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$. Finally obtain and plot the histogram  $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|\lambda \text{ uncertain})$. 
%    \item Fixed the $\lambda$ to be $\mathbb{E}(\lambda)$ and all $E_i$ to be $\mathbb{E}(E_i)$.     Then $J_{ij}$ is sampled from the normal distribution $\log_{10}(J_{ij}^2) \in \mathcal{N}(\mathbb{E}(\log_{10}(J_{ij}^2)), \mathbb{V}(\log_{10}(J_{ij}^2)))$. Finally obtain and plot the histogram  $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$.
%    \item Both $E_i$, $\lambda$ and $J_{ij}$ are sampled from their normal distribution:

%    $\lambda_i \in \mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$,

%    $E_i \in \mathcal{N}(\mathbb{E}(E), \mathbb{V}(E))$,

%    $\log_{10}J_{ij}^2 \in \mathcal{N}(\mathbb{E}(\log_{10}J_{ij}^2), \mathbb{V}(\log_{10}J_{ij}^2))$.
%    Then obtain and plot the histogram $N_\text{MC}$ sample of $\tau$, whose distribution is denoted as the following distribution: 
%    $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$.
%\end{enumerate}

%The analytical forms of the distribution $P_\lambda(\log_{10}(\tau))$, $P_E(\log_{10}(\tau))$, $P_J(\log_{10}(\tau))$ and $P_\mathbf{x}(\log_{10}(\tau))$ are usually unknown. 
%To quantify the uncertainty and variability in the sample data, we calculate a $99\%$ confidence interval around the median. 
%This statistical quantity is typically nonparametric, and relies on percentiles of the data, making it robust to different types of probability mass function.

%Using the equal-tailed percentile method, its calculation involves sorting the data and determining percentiles that correspond to the desired confidence level.
%Given a dataset $\{ \tau_1, \tau_2, \dots, \tau_n \}$, the procedure can be described as follows:
%\begin{enumerate}
%  \item Sort the data in ascending order. For a confidence level $CL$, the corresponding complement 
%  $1-CL$ determines the tails of the interval. 
%  \item Find the lower bound $\tau_{\eta}$ corresponds to the $\eta$-th percentile of the dataset where $\eta = (1-CL)/2$. For a $99\%$ confidence interval, $\eta=0.05$.
%  \item Find the upper bound $\tau_{(1-\eta)}$ corresponds to the $(1-\eta)$-th percentile of the dataset.
%  \item The confidence interval around the median is $[\tau_{\eta}, \tau_{(1-\eta)}]$.
%\end{enumerate}

@@

%Figure .\ref{fig:mle_MADN_withE}(b) shows that $\log_{10}(\tau)$ has a confidence interval of -8.0 to -7.4 when $\lambda$ is varied. 
%Figure \ref{fig:mle_MADN_withE}(c) show that when $J_{ij}$ is uncertain $\log_{10}(\tau)$ has a narrow confidence interval of -7.9 to -7.7, suggesting that the variation in $J_{ij}$ leads to relatively small change in $\log_{10}(\tau)$ compared to $E_i$ and $\lambda$.

%
%\begin{figure}[t]
%  \centering
%  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_noE.pdf}
%  \caption{\bjoern{TODO Zhong:}{these should also strictly be $\log_{10}(\tau/\unit[]{s})$.}Distribution of ToFs in the multiscale modeled MADN system.
%  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution. The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
%  Energy disorder is not consider. 
%  The black circles indicate the ToF obtained using varying HFX values.
%  (a) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
%  (b) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
%  (c) $P(\log_{10}(\tau)|\lambda, J_{ij} \text{ uncertain})$. }
%  \label{fig:mle_MADN_noE}
%\end{figure}
%

%When the energy disorder in MADN system is not considered, that is, all the MADN molecule energy are set to be equal giving $\Delta E=0$, the distribution of ToF is shown in Fig.\ref{fig:mle_MADN_noE}. 
%The distribution $P(\log_{10}(\tau)|\lambda \text{ uncertain})$ has a range of confidence interval -9.6 to -9.0 resembles that of $P(\log_{10}(\tau)|\lambda, J_{ij} \text{ uncertain})$, which has a range of confidence interval -9.7 to -9.1.

%\subsection{Sobol indices}
Besides the inspection on the distributions for various uncertain parameter (sets) as above, one can also quantify the sensitivity of the time-of-fight to the respective parameters by evaluating their contributions to the overall observed variance in $\tau$. One way of decomposing the variance of the model output into fractions attributed to input parameters is the variance-based sensitivity analysis using Sobol indices~\cite{saltelli_variance_2010}.

@@

%\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
%\caption{\label{tab:Sobol}%
%Sobol indices of $\lambda$, $E$ and $\log_{10} J^2$ when ToF is calculated with energy disorder, and Sobol indices of $\lambda$ and $\log_{10} J^2$ when ToF is calculated without energy disorder.
%}
%\begin{ruledtabular}
%  \begin{center}
%    \begin{tabular}{c c c c c c c} %\hline
%      &  \multicolumn{3}{c}{\bf Energy Disorder} & &\multicolumn{2}{c}{\bf no Disorder}\\\cline{2-4}  \cline{6-7}
%      parameter  & $\lambda$ & $ E_i$ & $ \log_{10}(J_{ij}^2)$ && $\lambda$ & $ \log_{10}(J_{ij}^2)$ \\ \hline
      %\multicolumn{6}{c}{\bf GRW for $\mathbf{N_c=1}$}\\
%   $S_T$  & 0.097 & 0.95 & 0.018 && 0.96 & 0.11 \\
%    \end{tabular}
%  \end{center}
%\end{ruledtabular}
%\end{table}
%

%From table \ref{tab:Sobol} one can see that most of the total variance can be attributed to the energy $E$. In contrast to $E$, the uncertainty in $\lambda$ and $\log_{10} J^2$ contributes much less compared to $E$, this is consistent to the Fig.\ref{fig:mle_MADN_withE}, where the distribution in Fig.\ref{fig:mle_MADN_withE}(d) resembles the distribution in Fig.\ref{fig:mle_MADN_withE}(a).
%And Fig.\ref{fig:mle_MADN_withE}(c) shows that the uncertainty in $\log_{10}(J^2)$ only leads to small variances.
%When there is no energy disorder, the variance in $\lambda$ has the most contribution to the total variance as shown in Table \ref{tab:Sobol}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\begin{figure}
%  \centering
%  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_withE_SS.pdf}
%  \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN.
%  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
%  The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
%  The black circles indicate the $v_\text{SS}$ obtained using varying HFX values.
%  (a) $P(\log_{10}(v_\text{SS})|E_i \text{ uncertain})$, 
%  (b) $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$, 
%  (c) $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$, 
%  (d) $P(\log_{10}(v_\text{SS})|E_i, \lambda, J_{ij} \text{ uncertain})$. }
%  \label{fig:mle_MADN_withE_SS}
%\end{figure}
%
%
%\begin{figure}
%  \centering
%  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_noE_SS.pdf}
%  \caption{Distribution of steady state velocity $v_\text{SS}$ in the multiscale modeled MADN. All molecule energies are set to be zero.  
%  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution.
%  The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
%  The black circles indicate the $v_\text{SS}$ obtained using varying HFX values.
%  (a) $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$, 
%  (b) $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$, 
%  (c) $P(\log_{10}(v_\text{SS})|\lambda, J_{ij} \text{ uncertain})$.  }
%  \label{fig:mle_MADN_noE_SS}
%\end{figure}

%\section{Distribution of Steady State Velocity}

%The distribution of steady state velocity of MADN is shown as Fig.\ref{fig:mle_MADN_withE_SS} and \ref{fig:mle_MADN_noE_SS}. 
%From the confidence interval, $P(\log_{10}(v_\text{SS})|E_i \text{ uncertain})$ has a range of -2.6 to -0.9, and the confidence interval $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$ has a range from -1.7 to -1.1. The width of those confidence intervals is very close to the confidence interval of distributions $P(\log_{10}(\tau)|E_i \text{ uncertain})$ and $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, respectively.
%However, $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$ has a range from -1.6 to 1.3, spanning 3 orders of magnitude. This is  much larger than $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$ as shown in Fig .\ref{fig:mle_MADN_withE}.  
%The large confidence interval in $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$ shows that $v_{ss}$ is very sensitive to the change in $J_{ij}$. Combining all the uncertainty effects in $E_i, \lambda, J_{ij}$, the confidence interval of $P(\log_{10}(v_\text{SS})|E_i, \lambda, J_{ij} \text{ uncertain})$ is from -2.5 to 1.3, covering 4 orders of magnitude.

%When energy disorder is not considered, the $v_\text{SS}$ distribution $P(\log_{10}(v_\text{SS})|\lambda, J_{ij} \text{ uncertain})$ has a confidence interval from 0.3 to 3.5, spanning 3 orders of magnitude. This interval is close to the range of $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$ when only $J_{ij}$ is uncertain. 
%In contrast, the interval of $P(\log_{10}(v_\text{SS})|\lambda \text{ uncertain})$ is from 0.6 to 1.2, whose width is much smaller than that of $P(\log_{10}(v_\text{SS})|J_{ij} \text{ uncertain})$.

%These result suggests that compared to the ToF $\tau$, the quantity $v_\text{SS}$ is significantly affected by uncertainties in $J_{ij}$, so $v_\text{SS}$ is less robust when the parameters $E_i, \lambda, J_{ij}$ contains uncertainty at the same time. 
%In the next section, the Poole–Frenkel behavior, that is the dependence of charge mobility on the electric field will be study using the ToF setting. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Drift-diffusion Charge mobility}
When an external electric field, $\mathbf{F}$, is applied to the system, the transport is not just diffusive but a drift-diffusion process. The material property of interest is then the drift mobility
%
\begin{equation}
    \mu = \frac{\mathbf{v} \mathbf{F} }{ |\mathbf{F}|^2},
    \label{eq:mu}
\end{equation}
%
where $\mathbf{v} = \mathbf{s}/{\tau}$ is the effective velocity of the charge carrier and $\mathbf{s}$ is the vector connecting the initial and final positions of the charge carrier. Here, we perform calculations for six different field directions (positive and negative Cartesian directions) with the source and sink conditions set accordingly. The electric field is taken account in the Marcus rate in Eq.~\ref{equ:Marcus} via an additional term in $\Delta E_{ij}$ given by $e\mathbf{F} \cdot \mathbf{r}_{ij}$, where $\mathbf{r}_{ij}$ connects the center-of-masses (COMs) of molecules $i$ and $j$. Finally, we define for a certain field strength $F=\vert\mathbf{F}\vert$ the ToF drift mobility $\mu(F)$ is as the average over the six directions.

@@

We perform such mobility calculations for the six explicit \ahfx models as well as the Monte-Carlo sampled uncertainty for six different values of $F$. The results are shown in Fig.~\ref{fig:fig_mle_withE_mu2_ave}. While the distributions shift depending on the strength of the applied field, the overall shape and the width of the confidence intervals is very similar. The width of the confidence intervals in $\log_{10}(\mu)$ decreases from \unit[0.9]{} at low fields ($\unit[4 \cdot 10^7]{V/m}$) to \unit[0.7]{} at a field of $\unit[9 \cdot 10^7]{V/m}$, corresponding broadly to a width of close to one order of magnitude in $\mu$. A stronger drift component due to a larger external electric field seems to make the mobility slightly less sensitive to uncertainties \bjoern{CHECK}{not sure about this interpretation}.

@@

\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
  \caption{\label{tab:PF_parameter}%
  Poole-Frenkel parameters $\mu_0$ (in $\unit[]{cm^2/(Vs)}$) and $\beta$ (in $\unit[]{\sqrt{cm/V}}$) of the multiscale modeled MADN, calculated by the six different \ahfx values. 
  }
  \begin{ruledtabular}
    \begin{tabular}{c c c}
    $\ahfx$ & $\mu_0$  & $\beta$ \\
      \hline
    0 & $4.0 \cdot 10^{-3}$ & $1.0 \cdot 10^{-3}$ \\
    0.05 & $2.1 \cdot 10^{-3}$ & $9.3 \cdot 10^{-4}$ \\
    0.10 & $1.0 \cdot 10^{-3}$ & $1.5 \cdot 10^{-3}$ \\
    0.15 & $8.0 \cdot 10^{-4}$ & $1.6 \cdot 10^{-3}$ \\
    0.20 & $9.3 \cdot 10^{-4}$ & $1.3 \cdot 10^{-3}$ \\
    0.25 & $2.6 \cdot 10^{-4}$ & $1.8 \cdot 10^{-3}$ \\
      \end{tabular}
  \end{ruledtabular}
  \end{table}

@@

\section{Discussion \& Conclusion}
One key observation of this study of Uncertainty Quantification in multiscale models for charge transport in organic semiconductors due to the choice of exchange-correlation functionals in density functional theory by systematically varying the Hartree--Fock exchange fraction in hybrid functionals is the dominance of site energy uncertainties in influencing the variability of the time-of-flight (ToF) and mobility predictions. In contrast, the uncertainties in reorganization energies and electronic coupling elements are shown to have a relatively minor effect. This suggests that further efforts to enhance the accuracy of site energy calculations -- potentially through improved parameterization or advanced quantum mechanical methods -- could significantly improve the reliability of multiscale modeling predictions.   Interestingly, the results also demonstrate that the uncertainties in electronic coupling elements, particularly those with very small magnitudes, are less relevant for overall charge transport. This aligns with the percolation analysis, which indicates that coupling elements below a critical threshold contribute minimally to the connectivity of the charge transport network. Thus, simplifying approximations in handling these low-value couplings could be justified in specific scenarios to reduce computational complexity without compromising accuracy.

>>>>

@@

\begin{table}[tbp]
  \caption{Characteristics of site energies $E$ (all in \unit[]{eV}) obtained for the different values of \ahfx : minimum ($E_\text{min}$) and maximum ($E_\text{max}$), the overall standard deviation and the contributions for static and polar calculations, as well as the largest absolute variation $D_{\ahfx}$ with respect to the PBE0 data ($\ahfx=0.25$).}
  \begin{ruledtabular}
    \begin{tabular}{c c c c c c c}
    $\ahfx$ & $E_\text{min}$ & $E_\text{max}$ & $\sigma$ & $\sigma_\text{el}$ & $\sigma_\text{polar}$ &  $D_{\ahfx}$ \\
    \hline
    0    & -1.11 & -0.59 & 0.08 & 0.10 & 0.04 & 0.13 \\ 
    0.05 & -1.07 & -0.63 & 0.07 & 0.09 & 0.04 & 0.12 \\ 
    0.10 & -1.13 & -0.61 & 0.08 & 0.10 & 0.04 & 0.13 \\ 
    0.15 & -1.16 & -0.59 & 0.09 & 0.11 & 0.05 & 0.15 \\ 
    0.20 & -1.12 & -0.63 & 0.08 & 0.10 & 0.05 & 0.12 \\ 
    0.25 & -1.17 & -0.60 & 0.08 & 0.11 & 0.04 & ---  \\ 
    \end{tabular}
  \end{ruledtabular}
  \label{tab:maxEi}
\end{table}

@@

\begin{table}[tbp]
\caption{Simulated ToF (in \unit[]{s}) for different values of \ahfx in the full graph, with an additional cutoff on $J^2$, and for the case with no energetic disorder, respectively.}
\begin{ruledtabular}
  \begin{tabular}{c c c c }
        \ahfx & full & $J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > -5)$ & $\Delta E_{ij} =0$ \\
    \hline
        0.00 &  $6.4 \cdot 10^{-9}$ & $7.5 \cdot 10^{-9}$ & $1.9 \cdot 10^{-10}$ \\
        0.05 & $ 7.9 \cdot 10^{-9}$ & $8.1 \cdot 10^{-9}$ & $4.1 \cdot 10^{-10}$ \\
        0.10 & $ 1.6 \cdot 10^{-8}$ & $1.6 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\
        0.15 & $ 3.0 \cdot 10^{-8}$ & $3.1 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\
        0.20 & $ 2.1 \cdot 10^{-8}$ & $2.5 \cdot 10^{-8}$ & $4.5 \cdot 10^{-10}$ \\
        0.25 & $ 9.5 \cdot 10^{-8}$ & $9.7 \cdot 10^{-8}$ & $7.2 \cdot 10^{-10}$ \\
    \end{tabular}
\end{ruledtabular}
\label{tab:ToF_MADN_HFX}
\end{table}

From the analysis of reorganization energies, site energies, and electronic coupling elements for different values of \ahfx, it is not clear how the mostly on distribution-level observed variations impact the overall charge transport properties. To scrutinize the dependence of such a material property, we now calculate the time-of-flight $\tau$ and report the respective values in Table~\ref{tab:ToF_MADN_HFX}. Here, we refer with ''full'' to time-of-flight obtained for the as-calculated charge transport network. One can see that $\tau$ varies by roughly one order of magnitude between $\ahfx=0$ ($\unit[6.3\cdot 10^{-9}]{s}$) and $\ahfx=0.25$ ($\unit[9.5\cdot 10^{-8}]{s}$), with an almost monotonous increase. When the squared coupling elements with values below $\unit[10^{-5}]{(eV)^2}$ are set to zero ($J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > -5)$), one obtains only minimally, but consistently, larger $\tau$, corroborating the notion that the very small coupling elements are of little relevance for charge transport. Finally, we also consider the case in which the energetic disorder is ignored ($\Delta E_{ij}=0$). Here, one also can see (next to the generally shorter time-of-flight) a consistent increase in $\tau$, however only by a factor of about \unit[3.8]{}, a combined effect of the increased reorganization energy and variations in coupling elements.

@@

Because the precise distribution of the uncertainties of the $M$ parameters is not known, we consider the maximum amount of uncertainties from a maximum likelihood estimation based on the data obtained from the explicit results for the different values of \ahfx and the assumption of normal distributions. In other words, each of the parameters $x_i$ for $i=1,\ldots,M$ is assigned a normal distribution with $\mathcal{N}(\mathbb{E}(x_i),\mathbb{V}(x_i))$, with $\mathbb{E}(x_i)$ ($\mathbb{V}(x_i)$) the mean (variance) of the respective data. Then, Monte-Carlo sampling is used to obtain $N_\text{MC}=50000$ different realizations of $\mathbf{x}$, the respective time-of-flight is calculated from these samples, and the resulting distribution $P(\log_{10}(\tau))$ is statistically analyzed. Specifically, we consider four different settings: in three settings, only one of the parameters blocks $(\lambda,\left\{E\right\},\left\{\log_{10}(J^2)\right\})$ is sampled while the values of the other blocks are set to their respective mean values, and we denote the resulting distributions as $P_\lambda(\log_{10}(\tau))$, $P_E(\log_{10}(\tau))$, and $P_J(\log_{10}(\tau))$, respectively. In the fourth setting, all parameters are sampled at the same time, yielding $P_\mathbf{x}(\log_{10}(\tau))$. As these distributions do not necessarily follow any specific analytic form, we estimate a $99\%$ confidence interval around the median using the equal-tailed percentile method.

@@

@@

We note that the above analysis from sampling via independent distributions of the uncertain parameters assumes that the parameters themselves are independent or uncorrelated. Correlations in organic semiconductors are typically found among the site energies when the molecules are polar~\cite{Baumeier2011,10.1063/5.0049513}. MADN has a very low dipole moment, and we find practically no spatial correlations between the site energies, making the sampling approach suitable for this material system.

Besides the inspection on the distributions for various uncertain parameter (sets) as above, one can also quantify the sensitivity of the time-of-fight to the respective parameters by evaluating their contributions to the overall observed variance in $\tau$. One way of decomposing the variance of the model output into fractions attributed to input parameters is the variance-based sensitivity analysis using Sobol indices~\cite{saltelli_variance_2010}.

@@

\subsection{Drift-diffusion Charge mobility}
When an external electric field, $\mathbf{F}$, is applied to the system, the transport is not just diffusive but a drift-diffusion process. The material property of interest is then the drift mobility
%
\begin{equation}
    \mu = \frac{\mathbf{v} \mathbf{F} }{ |\mathbf{F}|^2},
    \label{eq:mu}
\end{equation}
%
where $\mathbf{v} = \mathbf{s}/{\tau}$ is the effective velocity of the charge carrier and $\mathbf{s}$ is the vector connecting the initial and final positions of the charge carrier. Here, we perform calculations for six different field directions (positive and negative Cartesian directions) with the source and sink conditions set accordingly. The electric field is taken account in the Marcus rate in Eq.~\ref{equ:Marcus} via an additional term in $\Delta E_{ij}$ given by $e\mathbf{F} \cdot \mathbf{r}_{ij}$, where $\mathbf{r}_{ij}$ connects the center-of-masses of molecules $i$ and $j$. Finally, we define for a certain field strength $F=\vert\mathbf{F}\vert$ the ToF drift mobility $\mu(F)$ is as the average over the six directions.

@@

We perform such mobility calculations for the six explicit \ahfx models as well as the Monte-Carlo sampled uncertainty for six different values of $F$. The results are shown in Fig.~\ref{fig:fig_mle_withE_mu2_ave}. While the distributions shift depending on the strength of the applied field, the overall shape and the width of the confidence intervals is very similar. The width of the confidence intervals in $\log_{10}(\mu)$ decreases from \unit[0.9]{} at low fields ($\unit[4 \cdot 10^7]{V/m}$) to \unit[0.7]{} at a field of $\unit[9 \cdot 10^7]{V/m}$, corresponding broadly to a width of close to one order of magnitude in $\mu$. A stronger drift component due to a larger external electric field seems to make the mobility slightly less sensitive to uncertainties.

@@

\begin{table}[tbp]
  \caption{\label{tab:PF_parameter}%
  Poole-Frenkel parameters $\mu_0$ (in $\unit[]{cm^2/(Vs)}$) and $\beta$ (in $\unit[]{\sqrt{cm/V}}$) of the multiscale modeled MADN, calculated by the six different \ahfx values. 
  }
  \begin{ruledtabular}
    \begin{tabular}{c c c}
    $\ahfx$ & $\mu_0$  & $\beta$ \\
      \hline
    0 & $4.0 \cdot 10^{-3}$ & $1.0 \cdot 10^{-3}$ \\
    0.05 & $2.1 \cdot 10^{-3}$ & $9.3 \cdot 10^{-4}$ \\
    0.10 & $1.0 \cdot 10^{-3}$ & $1.5 \cdot 10^{-3}$ \\
    0.15 & $8.0 \cdot 10^{-4}$ & $1.6 \cdot 10^{-3}$ \\
    0.20 & $9.3 \cdot 10^{-4}$ & $1.3 \cdot 10^{-3}$ \\
    0.25 & $2.6 \cdot 10^{-4}$ & $1.8 \cdot 10^{-3}$ \\
      \end{tabular}
  \end{ruledtabular}
  \end{table}

@@

\section{Discussion \& Conclusion}
One key observation of this study of Uncertainty Quantification in multiscale models for charge transport in organic semiconductors due to the choice of exchange-correlation functionals in density functional theory by systematically varying the Hartree--Fock exchange fraction in hybrid functionals is the dominance of site energy uncertainties in influencing the variability of the time-of-flightand mobility predictions. In contrast, the uncertainties in reorganization energies and electronic coupling elements are shown to have a relatively minor effect. This suggests that further efforts to enhance the accuracy of site energy calculations -- potentially through improved parameterization or advanced quantum mechanical methods -- could significantly improve the reliability of multiscale modeling predictions.   Interestingly, the results also demonstrate that the uncertainties in electronic coupling elements, particularly those with very small magnitudes, are less relevant for overall charge transport. This aligns with the percolation analysis, which indicates that coupling elements below a critical threshold contribute minimally to the connectivity of the charge transport network. Thus, simplifying approximations in handling these low-value couplings could be justified in specific scenarios to reduce computational complexity without compromising accuracy.
